\textbf{1. Every one is a sinner}

Romans 3:10: As it is written, There is none righteous, no, not one

Romans 3:23: For all have sinned, and come short of the glory of God


\textbf{2. Every one deserves to go to hell}

Romans 6:23: For the wages of sin is death; but the gift of God is eternal life through Jesus Christ our Lord

Revelation 20:14-15:  And death and hell were cast into the lake of fire. This is the second death.  And whosoever was not found written in the book of life was cast into the lake of fire

Revelation 21:8:  But the fearful, and unbelieving, and the abominable, and murderers, and whoremongers, and sorcerers, and idolaters, and all liars, shall have their part in the lake which burneth with fire and brimstone: which is the second death.


\textbf{3. Jesus died for our sins according to the scriptures; he was buried, and he rose again the third day according to the scriptures:}

Romans 5:8 But God commendeth his love toward us, in that, while we were yet sinners, Christ died for us.

1 Peter 2:24: Who his own self bare our sins in his own body on the tree, that we, being dead to sins, should live unto righteousness: by whose stripes ye were healed.


\textbf{4. You must believe on Jesus Christ as your only way to heaven}

Acts 16:31  And they said, Believe on the Lord Jesus Christ, and thou shalt be saved, and thy house.

John 3:16  For God so loved the world, that he gave his only begotten Son, that whosoever believeth in him should not perish, but have everlasting life.


\textbf{5. When you believe on Jesus Christ, God gives you eternal life (a gift illustrates eternal security)}

Romans 6:23  For the wages of sin is death; but the gift of God is eternal life through Jesus Christ our Lord.


\textbf{Questions}

  1. Do you believe that you have sinned?

  2. Do you believe that Jesus Christ died on the cross for your sins and rose again from the dead?

  3. If you were to ask Jesus to save you right now would he do it?

  4. How long would you be saved for?

\textbf{If understood}

{\em "Dear Jesus, I know I am a sinner, and I know I deserve to go to hell.  But I
believe that you died on the cross for my sins. Please save me and take me to
heaven when I die. I'm trusting only you, Jesus. Amen." }

Romans 10:13 For whosoever shall call upon the name of the Lord shall be saved.

John 5:24 Verily, verily, I say unto you, He that heareth my word, and
believeth on him that sent me, hath everlasting life, and shall not come into
condemnation; but is passed from death unto life.

